---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

# melbWeather

<!-- badges: start -->
<!-- badges: end -->

[pkgdown](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-tdew0002/) site.

The melbWeather package provides tools to analyze and visualize Melbourne's weather data, including minimum and maximum temperature trends over time. It is designed for students and analysts looking to explore temperature patterns in a user-friendly way using R and Shiny.

## Installation

You can install the development version of melbWeather from GitHub with: [GitHub](https://github.com/ETC5523-2024/assignment-4-packages-and-shiny-apps-tdew0002) with:

``` {r, eval = FALSE}
# Install the 'remotes' package if you haven't already
install.packages("remotes")
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-tdew0002")
```


## Getting Started
Load the package with:
```{r}
library(melbWeather)
```

### Cleaning Raw Weather Data
The clean_weather_data() function is created and used to clean raw weather data files before performing analysis. Here’s an example of how to use it:
```{r, eval = FALSE}
# Assuming you have raw CSV files for minimum and maximum temperatures
min_temp_path <- "data-raw/melbourne_weather_min.csv"
max_temp_path <- "data-raw/melbourne_weather_max.csv"

# Clean the data using the clean_weather_data function
weather_data <- clean_weather_data(min_temp_path, max_temp_path)

# View the first few rows of the cleaned data
head(weather_data)
```

The clean_weather_data() function combines the data from both files, standardises column names, and formats dates for further analysis.

### Weather data
User does not need to use the clean_weather_data() function, instead the dataset created by clean_weather_data() function in this package can be directly access by using weather_data, which contains daily weather records for Melbourne, including minimum and maximum temperatures.

```{r}
# Load Melbourne weather data
data("weather_data")

# Display the first few rows of the data
head(weather_data)
```

## Example Analysis

Here is an example of summarising a basic dataset:
```{r}
summary(weather_data$minimum_temperature_degree_c)
```

You can also embed plots, for example:
```{r}
library(ggplot2)
ggplot(weather_data, aes(x = as.Date(paste(year, month, day, sep = "-")), y = minimum_temperature_degree_c)) +
  geom_line(color = "#005b96") +
  labs(
    title = "Minimum Temperature Trend in Melbourne",
    x = "Date",
    y = "Temperature (°C)"
  ) +
  theme_minimal()

```

## Launch the Shiny App
The `melbWeather` package includes an interactive Shiny app for exploring weather data. You can access the app directly online:

[Launch the Interactive Shiny App](https://tycia.shinyapps.io/melbWeatherApp/)

To run the app locally, use the following command:
```{r, eval = FALSE}
# Launch the Shiny app
startApp()
```

## Vignettes
For a detailed tutorial and examples on how to use melbWeather, check out the vignette:
```{r}
# View the vignette after installing the package
vignette("melbWeather-introduction")
```
The vignette provides step-by-step instructions on how to clean weather data, use the interactive Shiny app, and perform analyses with the melbWeather package.

Or read it online at the [pkgdown](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-tdew0002/) site.

## License 
This package is licensed under the MIT License. See the LICENSE file for more information.

## Aknowledgement
Data for this package is sourced from the [Australian Bureau of Meteorology](http://www.bom.gov.au/).

### Key Sections of the `README.Rmd`

1. **Package Introduction**: Provides a brief overview of what the `melbWeather` package does.
2. **Installation**: Includes instructions for installing the package using `remotes`.
3. **Getting Started**: Shows how to load the package and access the main dataset.
4. **Example Analysis**: Demonstrates a simple plotting example using `ggplot2` and the `weather_data` dataset.
5. **Shiny App**: Explains how to launch the Shiny app locally and provides a link to the online version hosted on `shinyapps.io`.
6. **Documentation and Vignettes**: Directs users to the `pkgdown` site for full documentation and tutorials.
7. **License and Acknowledgements**: Mentions the license and credits the data source.

