---
title: "melbWeather-introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{melbWeather-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The `melbWeather` package provides tools to analyze and visualize Melbourne's weather data, including minimum and maximum temperature trends. This vignette will guide you through the basic usage of the package.

## Installation

Install the development version of the package from GitHub:

```{r}
# install.packages("remotes")
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-tdew0002")
```

## Loading the Package 

```{r setup}
library(melbWeather)
```

## Cleaning Data
Use the clean_weather_data function to clean raw weather data files:
```{r}
# Example file paths (adjust these paths to your own data)
min_temp_path <- "data-raw/melbourne_weather_min.csv"
max_temp_path <- "data-raw/melbourne_weather_max.csv"

# Clean the data
cleaned_data <- clean_weather_data(min_temp_path, max_temp_path)
head(cleaned_data)
```

## Launching the Shiny App
This Shiny app allows users to filter Melbourne temperature data by date range and temperature type, providing an interactive way to visualize trends.
Launch the interactive Shiny app to explore weather trends:
```{r}
startApp()
```
