---
title: "Introduction to melbWeather"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to melbWeather}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  eval = FALSE
)
```

## Introduction
This vignette introduces the melbWeather package, which provides tools for analyzing and visualizing Melbourne's weather data.

## Overview
Welcome to the melbWeather package! This package is designed to help you analyze and visualize historical weather data for Melbourne, Australia. It provides functions for exploring temperature trends, weather summaries, and visualizations using daily minimum and maximum temperatures.

The melbWeather package comes with a built-in dataset called weather_data that includes daily weather records for Melbourne.

## Instalation 
To install the melbWeather package, use the following command in your R console:

```{r}
# Install the `remotes` package if you haven't already
install.packages("remotes")

# Install the `melbWeather` package from GitHub
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-tdew0002")
```

## Set Up
Once the package is installed, load it with:
```{r setup}
library(melbWeather)
```
## Example Usage
This vignette introduces the melbWeather package, which provides tools for analyzing and visualizing Melbourne's weather data.
```{r}
data("weather_data")
head(weather_data)
```

## Further Analysis
Use the functions in the melbWeather package to explore temperature trends:
```{r}
library(ggplot2)
ggplot(weather_data, aes(x = date, y = minimum_temperature_degree_c)) +
  geom_line() +
  labs(title = "Minimum Temperatures in Melbourne")
```

## Using the Shiny App
The melbWeather package also includes an interactive Shiny app for exploring the weather data. To launch the Shiny app, use the following function:

```{r}
# Launch the Shiny app
startApp()
```

The Shiny app provides interactive controls to filter data by date range and temperature type, making it easy to visualize trends and explore the dataset in detail.
